---
title: "Grace Darby - PS07"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r}
library(tidyverse)

alphabet_position <- tibble(
  letter = c("S", "A", "L", "M", "O", "N"),
  number = c(19, 1, 12, 13, 15, 14)
)

alphabet_position
```

## Including Plots

You can also embed plots, for example:

```{r, echo=TRUE}
ggplot(data = alphabet_position, mapping = aes(x = letter, y = number)) +
  geom_col(fill = "salmon") +
  labs(x = "Letter", y = "Position in Alphabet", title = "Letters in the Word Salmon by Position in Alphabet, Ascending Order") +
  theme(plot.title = element_text(hjust = 0.5))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
